\begin{thebibliography}{9}
\bibitem{andre}
Andresen A., (2015). Finite sample analysis of profile m-estimation in the single index model. \emph{Electronic Journal of Statistics}, 9(2):2528--2641. 
\bibitem{andresen}
Andresen, A., Spokoiny, V., (2015) Two convergence results for an alternation maximization. arXiv: 1501.01525v1
\bibitem{andres}
Andresen, A. and Spokoiny, V., (2013). Critical dimension in profile semiparametric estimation. 
\emph{Electronic Journal of Statistics}, 8(2):3077--3125, 2014. ISSN 1935-7524. doi: 10.1214/14-EJS982.
\bibitem{bezdek}
Bezdek, J., Hathaway, R. (2003). Convergence of Alternating Optimization. \emph{Neural, Parallel \& Pacific Computations 11}, 351 --- 368.  
\bibitem{cav_2}
Cavalier, L., Golubev, G. K., Picard, D., and Tsybakov, A. B. (2002). Oracle inequialities for inverse problems. \emph{The Annals of Statistics}, 30(3): 843 --- 874.
\bibitem{chen}
Chen, X. (2007). Large sample sieve estimation of semi-nonparametric models. \emph{Handbook of Econometrics}, 6:55495632.
\bibitem{chern}
Chernozhukov, V., Chetverikov, D., and Kato, K. (2014). Anti-concentration and honest, adaptive confidence bands. \emph{The Annals of Statistics}, 34(4):1653 --- 1677.
\bibitem{em}
A.P. Dempster, N.M. Laird, and D.B. Rubin (1977). Maximum likelihood from incomplete data via the EM algorithm. \emph{Journal of the Royal Statistical Society, Series B, 39:1 --- 38}.
\bibitem{gach}
Gach, F., Nickl, R., and Spokoiny, V. (2013). Spatially Adaptive Density Estimation by Localised Haar Projections. \emph{Annales de l'Institut Henri Poincare - Probability and Statistics}, 49(3): 900 --- 914. DOI: 10.1214/120-AIHP485; arXiv:1111.2807.
\bibitem{putnam}
Gelca, R., Titu, A., (2007). Putnam and beyond. \emph{Springer}, ISBN-13: 978-0-387-25765-5.
\bibitem{ibrag}
Ibragimov, I.A. and R.Z. Khas'minskij (1981). \emph{"Statistical estimation. Asymptotic theory. Translation from Russian by Samuel Kotz.".} "New York - Heidelberg - Berlin: Springer-Verlag". 
\bibitem{kneip}
Kneip, A., (1994). Ordered linear smoothers. \emph{The Annals of Statistics}, 22(2):835---866.
\bibitem{kosorok}
M. R. Kosorok. \emph{Introduction to Empirical Processes and Semiparametric Inference} (2005). \emph{Springer in Statistics}.
\bibitem{parni}
G. J. McLachlan and T. Krishman (1997). \emph{The EM Algorithm and Extensions.} Wiley, New York.
\bibitem{spok_12}
Spokoiny, V. (2012). Parametric estimation. Finite sample theory. \emph{Annals of Statistics}, 40(6):2877--2909.
\bibitem{spok_dick}
Spokoiny, V., Dickhaus, T., (2015). Basics of Modern Mathematical Statistics . \emph{Springer Texts in Statistics}.
\bibitem{spok_2013}
Spokoiny, V., Wang, W., and H\"ardle, W. (2013). Local quantile regression (with rejoinder). \emph{Journal of Statistical Planing and Inference,} 143(7):1109 --- 1129. arXiv:1208.5384.
\bibitem{tropp}
Tropp, J. A. (2012). User-friendly tail bounds for sums of random matrices. \emph{Foundations of Compution Mathematics,} 12.
\bibitem{tsyba} 
Tsybakov, A. (2000). On the best rate of adaptive estimation in some inverse problems. \emph{Comptes Rendus de l'Academie des Sciences - Series I - Mathematics,} 330(9):835 --- 840.
\bibitem{wu}
Wu, C. F. J. (1983). On the convergence properties of the EM algorithm. \emph{Annals of Statistics}, 11:95 --- 103.
\end{thebibliography}
