\documentclass[reqno,envcountsect,11pt]{svmono}
%\documentclass[aos,authoryear,dvips]{imsart}
\newcommand{\ifims}[2]{#1} % 1 - Latex, 2 - ims version
\newcommand{\ifAMS}[2]{#1}   % 1 - AMS, 2 - JEL
\newcommand{\ifAoS}[2]{#1}   % 1 - AoS, 2 - full
\newcommand{\ifau}[3]{#1}  % #1 - 1 author, #2 - 2 authors, #3 - 3 authors
\newcommand{\ifbook}[2]{#2}   % 1 - paper; 2 - book
\newcommand{\ifsv}[2]{#1} % springer version
%\newcommand{\ifsv}[2]{#2}   % latex version


\ifbook{
    \newcommand{\Chapter}[1]{\section{#1}}                                            
    \newcommand{\Section}[1]{\subsection{#1}}
    \newcommand{\Subsection}[1]{\subsubsection{#1}}
    \def\Chname{Section }
    \def\chname{section }
    \def\chapsect{Section}
  }
  {
    \newcommand{\Chapter}[1]{\chapter{#1}}
    \newcommand{\Section}[1]{\section{#1}}
    \newcommand{\Subsection}[1]{\subsection{#1}}
    \def\Chname{Chapter}
    \def\chname{chapter \,}
    \def\chapsect{Chapter}
  }


\def\thetitle{Nonparametric estimation: parametric view}
\def\theruntitle{Nonparametric estimation: parametric view}

\def\theabstract{
This monograph is based on the course of ``Nonparametric statistics'' 
I gave in the Fall 2014/2015 at the Humboldt university Berlin.
An important feature of this course is that it is almost self-contained,
only basic knowledge of probability theory and mathematical statistics 
are required.
A reader can consult my textbook on parametric theory for some additional reading.
The course is focused on the model choice.
First I discuss in details the model selection problem for a linear model.
Then I explain how the proposed approach can be applied to any regular model 
using the Fisher and Wilks expansions.
All the results in this course are recently developed and can only be found in 
in modern statistical literature. 
However, I tried to keep the derivation at the basic level with complete proofs 
and explanations.
The 
}


\def\kwdp{}
\def\kwds{}


\def\thekeywords{}

\def\thankstitle{}
\def\authora{Vladimir Spokoiny}
\def\thanksa{} 
\def\runauthora{spokoiny, v.}
\def\addressa{
    Weierstrass-Institute, \\ Humboldt University Berlin, \\ Moscow Institute of
    Physics and Technology
    \\
    Mohrenstr. 39, 10117 Berlin, Germany,    \\
    }
\def\emaila{spokoiny@wias-berlin.de}
\def\affiliationa{Weierstrass-Institute and Humboldt University Berlin}

\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[english]{babel}

\usepackage{enumerate}
%\usepackage{bbm}
%\usepackage{MnSymbol}
\usepackage{amsmath}
\usepackage{amssymb}
\ifsv{}{\usepackage{amsthm}}
\usepackage{natbib}
\usepackage{comment}
\usepackage{color}
\usepackage[mathscr]{eucal}
\usepackage[math]{easyeqn}
{   
    \numberwithin{equation}{chapter}
    \numberwithin{figure}{chapter}
}
\input mydef
%\input ../tex/statdef
\input statdef
%\input myMS
\usepackage{hyperref}
\hypersetup{linktocpage,
            colorlinks,
            linkcolor=hookersgreen,
            linktoc=blue,
            citecolor=ultramarine,
            urlcolor=black,
            filecolor=black
            }

\usepackage{nameref}
%%%%%%%%%%%%
\ifsv{}
{   
    \newcounter{example}[section]
    \numberwithin{example}{section}
    \newcounter{exercise}[section]
    \numberwithin{exercise}{section}
    \newcounter{remark}[section]
    \numberwithin{remark}{section}
    \newtheorem{theorem}{Theorem}[section]
    \newtheorem{proposition}[theorem]{Proposition}
    \newtheorem{lemma}[theorem]{Lemma}
    \newtheorem{corollary}[theorem]{Corollary}
    \newtheorem{definition}[theorem]{Definition}
    \newtheorem{exmp}[example]{Example}
    \newtheorem{rmrk}[remark]{Remark}
    \newtheorem{exrc}[exercise]{Exercise}
    \newenvironment{example}{\begin{exmp}\rm}{\end{exmp}}
    \newenvironment{remark}{\begin{rmrk}\rm}{\end{rmrk}}
    \newenvironment{exercise}{\begin{exrc}\rm}{\end{exrc}}
}

\renewcommand{\textfraction}{0.00}
\renewcommand{\topfraction}{1}
\renewcommand{\bottomfraction}{1}

\bibliographystyle{apalike}
\newcommand{\citeasnoun}[1]{\cite{#1}}

    \textheight=23cm
    \textwidth=14.8cm
    \topmargin=0pt
    \oddsidemargin=1.0cm
    \evensidemargin=1.0cm
    %\pagestyle{empty}
    \linespread{1.3}

%\includeonly{
%Ch_append,
%}
\allowdisplaybreaks
\begin{document}
\author{
Vladimir Spokoiny 
%Weierstrass Institute  and Humboldt University Berlin,} \\
%Mohrenstr. 39,
%10117 Berlin, Germany \\
%\texttt{ spokoiny@wias-berlin.de} 
}

\title{\thetitle}

\maketitle
\tableofcontents

\part{Model selection for linear methods}
\begin{quote}
\begin{flushright}                                      
\ldots 
the world will remain an eternal, 	\\
may be, comprehensible,				\\
but still endless.					\\[12pt]
J. Brodsky
\end{flushright}                                  
\end{quote}

\input{Ch_LR}
\input{Ch_LRrd}
\input{Ch_LE}
\input{Ch_LMSs} 
\input{Ch_LMSo} 
\input{Ch_LMSss} 
\input{Ch_LMSh} 
\input{Ch_LMSp} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%   new part   %%%%%%%%%%%%%%%%%%%%%%%%%
\part{General parametric theory}
\begin{quote}
\begin{flushright}                                      
\ldots And, then, there were only		\\
illusion and the road.				\\[12pt]
J. Brodsky
\end{flushright}                                  
\end{quote}

\input{Ch_FW}
\input{Ch_BvM}
\input{Ch_rough}
\input{Ch_semi}
\input{Ch_iid}
\input{Ch_GLM}
\input{Ch_ldens}
\input{Ch_regr}

\chapter{Median and quantile regression}
\chapter{Generalized regression}

%%%%%%%%%%%%%%%%%%%%%%%%%%%   new part   %%%%%%%%%%%%%%%%%%%%%%%%%
\part{Structural regression}

\input{Ch_sieveMS}

\part{Mathematical tools}
%\include{Ch_append}
\input{Ch_append}

\bibliography{exp_ts,listpubm-with-url,phdbib}
\end{document}
